The \dealii{} Library, Version 9.3

### 2021-06-17 9.3/paper.tex
write text (Sec 2.7 source based toolchain installer)
follow up

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Terminal based toolchain installer}
\label{subsec:candi}

Half a page up to a page on \candi.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Source based toolchain installer}
\label{subsec:candi}

The source based installation of \dealii{} or
complex toolchains of multiple libraries working together with \dealii{}
can be done with the \candi{} script tool. \candi is a bash-script based tool,
it is the abbreviation of ``compile and install'' and it is released under the
GNU LGPL v3.0.
%
The origin of \candi{} is a fork made in 2013 from \texttt{dorsal},
a retired source based installer for the \texttt{FEniCS} library.
%
The \candi{} tool can be found via the download page of \dealii{} since version 8.5
and is under continuous and active maintenance. To install older releases of
\dealii{} toolchains one can checkout the branch corresponding to the
\dealii{}-version with \texttt{git}.

The installer supports the user to download, unpack, compile and install a certain
library, a list of libraries or a complete toolchain.
A library is called a package within \candi{}.
The toolchain installation is the default behaviour and the default configuration
ensures that most of the \dealii{} step tutorials can be used directly.
The package installation mode can be handy to generate docker containers
for instance.
Especially in the toolchain mode we can check for dependencies from one library to
another and handle them accordingly.

Each package for a library is defined by variables for its name and version,
a (remote or local) download location,
its packaging format (e.g. tar, gz or zip),
a checksum to prevent from incomplete downloads,
its general build chain (e.g. using \texttt{autotools}, \texttt{cmake} and others)
as well as configuration options.
%
Moreover, one can give specific instructions for each of the steps being
necessary for the unpacking, configuration or building of the package.

An internet connection is not necessary for the run, if the source files
are downloaded and repositories are checked out to its unpacking location.
The download of a package can be supported via a local or remote mirror server
similar as we are doing it already for several of the packages.
%
If the temporary files of \candi{} are not removed, one can use a developer
mode to prepare patches or developments for any of the packages.
%
A new feature allows \candi{} to skip user prompts which can be used for
a batch mode run on a compute cluster job for instance.

This source based installer is implemented in a modular fashion. The main
script is implemented without any knowledge on a package or toolchain for
a specific operating system (platform).

The installer is organised in the following way:
\begin{itemize}
\item \texttt{candi.sh}: the bash-script which controls the overall process.

\item \texttt{candi.cfg} (or \texttt{local.cfg}): the default toolchain
configuration file. Here one can easily switch on/off important features,
give additional configuration options to \dealii{} and
define the set of packages for the toolchain.

\item \texttt{deal.II-toolchain} folder: the central project folder for
\dealii{}-based toolchains.
It contains subfolders for individual packages, platforms (operating systems)
and for patches to be applied after unpacking a package.

\end{itemize}

The \texttt{dealii/candi} \texttt{github} repository includes continuous
integration (CI) to ensure that new features of the script or new packages
are working as expected.
